Search-based Synthesis of Network Intrusion Detection Rules

### 2019-09-23 paper/paper.tex
pass on section II.B

The SYN Flood attack exploits a vulnerability in the TCP/IP handshake
to establish a TCP connection~\cite{cloudfare-synflood}. The handshake
works as follows. First, a client sends a SYN packet to the server,
requesting a connection. Second, the server responds with a SYN-ACK
packet to the client. Third, the client responds with an ACK message
and the connection is established. Aware of the protocol, an attacker
sends multiple SYN packets to different ports of a server, often using
fake IP addresses.\Mar{Are you saying that there is no timer that the
  server starts when it sends a SYN-ACK message?} Without proper protection, the server accepts the
connection requests and eventually legitimate connection requests
cannot be satisfied due to resource exhaustion.

>>>>

The SYN Flood attack exploits a vulnerability in the TCP/IP handshake
to establish a TCP connection~\cite{cloudfare-synflood}. The handshake
works as follows. First, a client sends a SYN packet to the server,
requesting a connection. Second, the server responds with a SYN-ACK
packet to the client. Third, the client responds with an ACK message
and the connection is established. Aware of the protocol, an attacker
sends multiple SYN packets to different ports of a server, often using
fake IP addresses. \Luc{Then, after the server responds with the usual SYN-ACK packet, the client sends another SYN to avoid the connection time out.} \Mar{Are you saying that there is no timer that the
  server starts when it sends a SYN-ACK message?} Without proper protection, the server accepts the
connection requests and eventually legitimate connection requests
cannot be satisfied due to resource exhaustion.
